---
title: "tues-inclass-work"
format: html
editor: visual
---

## Midterm Project Insight
Read in file using read.csv:

```{r}
strawberry <- read.csv(file = "strawb_mar6.csv")
```

Use functions created during last week (such as drop one val columns) to drop columns that either only have one data value or are all NA

Suggestion: split into two tables - one for census and one for survey, then split out state (and write functions to apply to the states); take apart the columns that have multiple things in one col (after splitting between census and survey)
```{r}
strawberry$Program |> unique() 
```

Other things to potentially use: tables, kable, kableExtra, plots (ggplot)

### Dictionary of Values in Data Set
Gain - someone bought an asset

## Coef of Variation
Often used in process control (how much "wiggling around" that occurs: 

```{r}
mean = 2
sd = 0.1 # how much variation is present in the data
from = mean - 4 * sd
to = mean + 4 * sd

x = seq(from = from, to = to, by = 0.01)
y = dnorm(x = x, mean = mean, sd =sd) # dnorm -> density func for norm dist
cvp <- (sd/mean) * 100
plot(x, y, type = "l", main = cvp)
```
CV % = Sn/Xn * 100
ex: 6.9 = (S/64,682,000) * 100 -> from strawberry dataset
 - so S (sd) = 4,463,000